\textcolor{red}{A Software Tool for building Suitable Datasets for Softcomputing and Machine Learning Techniques from Meteorological Data Integration}

### 2020-09-22 latex_manuscript/MDPI/2_energies_special_issue/template.tex
Cambios para el Special Issue de Energies

		A better understanding of the environment is of vital importance for science, contributing not only to more efficient exploitation of natural resources but also to the development of new strategies aimed at its protection. In that sense, meteorological observations provide an essential and valuable source of information which is widely used by researchers to address environmental learning, comprehension, prediction and conservation in numerous oceanic and atmospheric studies of a wide variety of areas (e.g. energy, climate change, agriculture, etc.). Some specific examples of the diversity of fields in which meteorological data can be used in are, among others: estimation of global solar radiation based on sunshine duration \cite{SHAHRUKHANIS2019179}, directional analysis of sea storms \cite{LAFACE201545}, assessment and control of wind turbine \cite{DAHHANI2018167}, wind power ramp events prediction \cite{DORADOMORENO2017428}, evaluation of salinity-gradient energy harvesting \cite{REYESMENDOZA2020100645}, study of the responses exhibited by plankton to fluid motions \cite{FUCHS2016109}, trends in solar radiation \cite{SILVA20101852} or simulation of extreme near shore sea conditions \cite{GOULDBY201415} \textcolor{red}{Poner o sustituir aquí por alguna referencia de Energies}. All these studies require a prior data collection and its adaptation to a specific format that allows the interpretation of them.

@@

		\textcolor{red}{Continuing with this line}, special purpose software is usually developed to help researchers to advance in their studies related to energy and environmental modelling, becoming a great support for decision-making in the exploitation and protection of the environment. In \cite{CAMARGONOGUEIRA2016361}, a software tool for designing solar water heating systems is developed, which simulates different situations and finds the best technical and economical solution. In \cite{LO2015293}, an integrated simulation tool for the optimum design of bifacial solar panel with reflectors is presented. This tool can also be used to analyse the performance of the solar cells. A framework for data integration of offshore wind farms is implemented in \cite{NGUYEN2013150} in order to facilitate data exchange and improve operation and maintenance practices. In \cite{SHEHADEH2020100644}, a load management application to maximize the used energy of thermal systems and reduce the costs and emissions is developed. A risk assessment tool to improve safety standards and emergency management in onshore wind farms, is presented in \cite{ASTIASOGARCIA201648}. Raabe et al. \cite{RAABE2010213} developed two software tools, \textit{Model of Equilibrium of Bay Beaches} (MEPBAY) and \textit{Coastal Modelling System} (SMC), to support different operational levels of headland-bay beach in coastal engineering projects, and Motahhir et al. \cite{MOTAHHIR20199} developed an open hardware/software test bench for solar tracker.

>>>>

		A better understanding of the environment is of vital importance for science, contributing not only to more efficient exploitation of natural resources but also to the development of new strategies aimed at its protection. In that sense, meteorological observations provide an essential and valuable source of information which is widely used by researchers to address environmental learning, comprehension, prediction and conservation in numerous oceanic and atmospheric studies of a wide variety of areas (e.g. energy, climate change, agriculture, etc.). Some specific examples of the diversity of fields in which meteorological data can be used in are, among others: estimation of global solar radiation based on sunshine duration \cite{SHAHRUKHANIS2019179}, directional analysis of sea storms \cite{LAFACE201545}, \textcolor{red}{estimation of hybrid energy systems taking into account economic and environmental objectives\cite{Kumar2020}}, wind power ramp events prediction \cite{DORADOMORENO2017428}, \textcolor{red}{sea surface temperature prediction \cite{He2020}}, study of the responses exhibited by plankton to fluid motions \cite{FUCHS2016109}, trends in solar radiation \cite{SILVA20101852} or simulation of extreme near shore sea conditions \cite{GOULDBY201415}. All these studies require a prior data collection and its adaptation to a specific format that allows the interpretation of them.

@@

		\textcolor{red}{de aqui quitar dos sobre la 9, la 12 y la 13}
		\textcolor{red}{Continuing with this line}, special purpose software is usually developed to help researchers to advance in their studies related to energy and environmental modelling, becoming a great support for decision-making in the exploitation and protection of the environment. In \cite{CAMARGONOGUEIRA2016361}, a software tool for designing solar water heating systems is developed, which simulates different situations and finds the best technical and economical solution. In \cite{LO2015293}, an integrated simulation tool for the optimum design of bifacial solar panel with reflectors is presented. This tool can also be used to analyse the performance of the solar cells. A framework for data integration of offshore wind farms is implemented in \cite{NGUYEN2013150} in order to facilitate data exchange and improve operation and maintenance practices. In \cite{SHEHADEH2020100644}, a load management application to maximize the used energy of thermal systems and reduce the costs and emissions is developed. A risk assessment tool to improve safety standards and emergency management in onshore wind farms, is presented in \cite{ASTIASOGARCIA201648}. Raabe et al. \cite{RAABE2010213} developed two software tools, \textit{Model of Equilibrium of Bay Beaches} (MEPBAY) and \textit{Coastal Modelling System} (SMC), to support different operational levels of headland-bay beach in coastal engineering projects, and Motahhir et al. \cite{MOTAHHIR20199} developed an open hardware/software test bench for solar tracker.
